Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-04 manuscript.Rmd
initial modeling:

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(rgdal)
library(tigris)
library(spdep)

@@

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE))
```

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(rgdal)
library(tigris)
library(spdep)
library(spatialreg)
library(ape)

@@

travel_time_sf <- travel_time_sf %>%
  mutate(distance = as.numeric(st_distance(centroids, mnm_sf$geometry, by_element = TRUE)))
```

@@

## Modeling

```{r}
week_1 <- travel_time_sf %>% filter(year == 2016, month == 9, week == 1)
```

```{r}
st_queen <- function(a, b = a) st_relate(a, b, pattern = "F***T****")
as.nb.sgbp <- function(x, ...) {
  attrs <- attributes(x)
  x <- lapply(x, function(i) { if(length(i) == 0L) 0L else i } )
  attributes(x) <- attrs
  class(x) <- "nb"
  x
}

Queen <- as.nb.sgbp(st_queen(week_1))
W <- nb2mat(Queen, style='B', zero.policy = TRUE)

plot(week_1["mean_travel_time"])
plot(Queen, week_1$centroids, col="blue", cex = 0.5, lwd = 0.5)
```

```{r CSR_test}
Moran.I(week_1$mean_travel_time, W, na.rm=TRUE)
```
